A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-08 paper.tex
Update Product Contract constructor

\lstdefinestyle{solidity}{
	captionpos=b,
	tabsize=4,
	basicstyle=\scriptsize
}
\lstset{style=solidity}
\begin{lstlisting}[caption={Product Contract data fields}, label={lst:constructor}, frame=single]
contract Product {
    address public broker;
    address public provider;
    bool isBrokerWithdraw;
    bool isProviderWithdraw;
    address[] consumers;
    address[] unsubscriber;

    struct Purchase {
        bool affirmativeVote;
        bool isConsumerWithdraw;
        bool isKeyAdded;
        string encryptKey;
    }
    mapping(address => Purchase) public consumer2Purchase;

    uint public price;
    uint public totalAmount;
    uint public brokerage;
    uint public threshold;
    string public channelRoot;
    string public endPoint;
    uint public totalNumber;
    uint public uploadedNumber;
    uint public affirmativeVotes;
    string hashedKey;
    string certifiedKey;

>>>>

\lstdefinestyle{solidity}{
	captionpos=b,
	tabsize=4,
	basicstyle=\scriptsize
}
\lstset{style=solidity}
\begin{lstlisting}[caption={Product Contract data fields}, label={lst:constructor}, frame=single]
contract Product {
    address public broker;
    address public provider;
    bool isBrokerWithdraw;
    bool isProviderWithdraw;
    address[] consumers;

    struct Purchase {
        bool affirmativeVote;
        bool isConsumerWithdraw;
        bool isKeyAdded;
        bool isSubscribe;
        string encryptKey;
    }
    mapping(address => Purchase) public consumer2Purchase;

    uint public price;
    uint public totalAmount;
    uint public brokerage;
    uint public cancellation;
    uint public threshold;
    string public channelRoot;
    string public endPoint;
    uint public totalNumber;
    uint public uploadedNumber;
    uint public affirmativeVotes;
    string hashedKey;
    string certifiedKey;
